Type-Safe Modular Parsing

### 2016-11-16 paper/sections/RelatedWork.tex
More.

- extensible parsing, language workbenches: rats, modular semantic actions, (syntactic modularity, no separate compilation, modular type-checking)
(read more papers, see if they talk about this issue, some potential solutions)

@@

>>>>

- extensible parsing, language workbenches: rats, noa (this one already uses OA), modular semantic actions, (syntactic modularity, no separate compilation, modular type-checking)
(read more papers, see if they talk about this issue, some potential solutions)

@@

noa, shy: shy: only override some interesting cases (transformation is tedious)
bruijn indices: parsing + transformation
